---
title: "MN COVID-19 Summary"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
library(knitr)
library(kableExtra)
library(lubridate)
## call other scripts
source('mdhCovidWebScrape.R')
source('COVID.R')

## get data for the most recent date
dataWidePlain = dataWide %>% 
   filter(Date == last(Date))

dataLongAvgPlain = dataLongAvg %>% 
   filter(Date == last(Date), Variable == "PositivePercent")

dataLongAvgPeople = dataLongAvg %>% 
   filter(Date == last(Date), Variable == "PositivePercentPeoplePlot")

```

## `r format(Sys.time(), '%Y-%m-%d')`
* Testing
  + Total number of completed tests: **`r (dataWidePlain$Total.tested) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$Daily.tests) %>% formatC(format="d", big.mark=",")`)
  + Total number of people tested: **`r (dataWidePlain$Total.tested.people) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$Daily.tests.people) %>% formatC(format="d", big.mark=",")`)
  + Total positive cases: **`r (dataWidePlain$Total.cases) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$New.cases) %>% formatC(format="d", big.mark=",")`)
  + Daily/7-day positive percentage: **`r (round(dataLongAvgPlain$Value, 4)*100)`/`r (round(dataLongAvgPlain$movAvgValue, 4)*100)`**
  <!-- + Daily/7-day positive percentage (people): **`r (round(dataLongAvgPeople$Value, 4)*100)`/`r (round(dataLongAvgPeople$movAvgValue, 4)*100)`** -->
* Case info   
  + Patients who are currently sick: **`r (dataWidePlain$Currently.sick) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.sick <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.sick))) %>% formatC(format="d", big.mark=",")`)
  + Total deaths: **`r (dataWidePlain$Total.deaths) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.deaths <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.deaths)))`)
* Hospital admission/Vaccine  
  + Total accumulated hospitalized: **`r (dataWidePlain$Total.Hospital) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.hospitalized <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.hospitalized))) %>% formatC(format="d", big.mark=",")`)
    - Total accumulated ICU: **`r (dataWidePlain$Total.ICU) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.ICU <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.ICU)))`)
  + Total accumulated vaccinated: **`r (dataWidePlain$Total.vaccine) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.vaccine <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.vaccine))) %>% formatC(format="d", big.mark=",")`)

```{r plot1, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p1
```

```{r plot2, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p2
```
   
```{r plot3, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p3
```

```{r plot5, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p5
```

```{r plot4, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p4
```

```{r plot6, echo=FALSE, warning = FALSE, message=FALSE}
## vaccination data
ggplot(data = dataWide %>% filter(Date > "2020-12-28"))+
  aes(x = Date)+
  geom_path(aes(y = Total.vaccine, color = "Total vaccine"), size = 1.5)+
  geom_col(aes(y = New.vaccine*p1Constant, fill = "New vaccine"))+
  scale_x_date(date_breaks = "7 days", date_labels = "%b %d")+
  scale_y_continuous(labels = scales::label_number_si(), sec.axis = sec_axis(~ ./(p1Constant), 		
                                                                             name = "New vaccination"))+
  labs(y = "Total accumulated vaccination", fill = "", x = "", title = "Vaccination data", color = "")+
  scale_fill_manual(values = alpha(RColorBrewer::brewer.pal(3, "Set1")[2],.5))+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),panel.grid.minor.x = element_blank(),legend.margin=margin(),legend.box="horizontal",legend.position = "bottom", axis.text.x = element_text(size=10, angle = 50, hjust = 1), text=element_text(size=14),legend.text = element_text(size=10))
```


```{r table1, echo=FALSE, warning= FALSE, include = FALSE}
## table 1
 dataWide %>% 
   mutate(Date = format(Date, format = "%b %d"))%>% 
   filter(Date %in% tail(Date, 5)) %>%
   select(-contains("By"),-contains("Plot")) %>% 
   select(Date, starts_with("Total")) %>%
   rename_at(vars(starts_with("Total")), ~str_to_title(str_remove_all(.,"Total."))) %>%
   kable(digits = 3,booktabs = T, caption = "Cumulative numbers for last 5 days",align = "c") %>%
   kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 14) %>% 
   row_spec(5, color = "white", background = "#FF33CC") 
```

```{r table2, echo=FALSE, warning= FALSE}
## table 2
 dataWide %>%
   mutate(Date = format(Date, format = "%b %d")) %>% 
   filter(Date %in% tail(Date, 7)) %>%
   select(-starts_with("Total"), -ends_with("Percent"), Daily.tests, Daily.tests.people) %>% 
   rename(`Hospitalized` = Currently.hospitalized, `New case` = New.cases, `Tests` = Daily.tests, `New people tested` = Daily.tests.people) %>%
   select(Date, Hospitalized, ICU, `New case`, Tests, `New people tested`) %>% 
   mutate_at(vars(Hospitalized:`New people tested`), list(~formatC(., format="d", big.mark=","))) %>%
   kable(digits = 2, booktabs = T, caption = "Current numbers for last 7 days", align = "c",linesep = "") %>%
   kable_styling(latex_options = c("hold_position","scale_down"), font_size = 14) %>%
   footnote(general = "https://github.com/coolbaby0208/MN-COVID19",general_title = "Source code: ",footnote_as_chunk = T) %>% 
   row_spec(7, color = "white", background = "#36688D")
```

