---
# title: "MN COVID-19 update: `r format(Sys.time(), '%Y-%m-%d')`  by r/coolbaby0208"
output: 
  pdf_document:
    fig_height: 5.5
    fig_width: 6
geometry: margin = 0.5in
spacing: single
papersize: letter
subparagraph: yes

editor_options: 
  chunk_output_type: console
classoption: twocolumn
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
## call "COVID.R"
source('COVID.R')

## get data for most recent date 
dataWidePlain = dataWide %>% 
  filter(Date == last(Date))
```

## MN COVID-19 Summary (`r format(Sys.time(), '%Y-%m-%d')`)
* Testing
  + Total number of completed tests: **`r (dataWidePlain$Total.tested)`** (up `r (dataWidePlain$Daily.tests)`)
  + Total positive: **`r (dataWidePlain$Total.cases)`** (up `r (dataWidePlain$New.cases)`)
* Case info   
  + Patients who are currently sick: **`r (dataWidePlain$Currently.sick)`** (`r (ifelse(dataWidePlain$New.sick <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.sick)))`
  + Total deaths: **`r (dataWidePlain$Total.deaths)`** (up `r (dataWidePlain$New.deaths)`)
 - Hospitalization   
   - Hospitalized as of today: **`r (dataWidePlain$Currently.hospitalized)`** (up `r (dataWidePlain$New.hospitalized)`)
     - Hospitalized in ICU as of today: **`r (dataWidePlain$ICU)`** (up `r (dataWidePlain$New.ICU)`)



```{r plot1, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p1
```


```{r plot2, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p2
```

   
```{r plot3, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p3
```


```{r table1, echo=FALSE, warning= FALSE}
 dataWide %>%
   filter(Date %in% tail(Date, 10)) %>%
   select(Date, starts_with("Total")) %>%
   rename_at(vars(starts_with("Total")), ~str_to_title(str_remove_all(.,"Total."))) %>%
   kable(digits = 3,booktabs = T, caption = "Total numbers for last 10 days",align = "c") %>%
   kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8) %>% 
   row_spec(10, color = "white", background = "#FF33CC")
```

```{r table2, echo=FALSE, warning= FALSE}
 dataWide %>%
   filter(Date %in% tail(Date, 10)) %>%
   #mutate(HospitalizedPercent = HospitalizedPercent*100, ICUPercent = ICUPercent*100) %>%
   select(-starts_with("Total"), -starts_with("New"), -ends_with("Percent"), Daily.tests) %>% 
   rename(`Hospitalized case` = Currently.hospitalized, `Active case` = Currently.sick, `ICU case` = ICU, `Daily tests` = Daily.tests) %>%
   select(Date, ends_with("case"), everything()) %>% 
   kable(digits = 2, booktabs = T, caption = "Current numbers for last 10 days", align = "c") %>%
   kable_styling(latex_options = c("scale_down","hold_position"), font_size = 8) %>% 
   row_spec(10, color = "white", background = "#FF33CC")
```

Data & source code:

* *https://www.health.state.mn.us/diseases/coronavirus/situation.html*
* *https://github.com/coolbaby0208/MN-COVID19*    

