---
title: "MN COVID-19 Summary"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
library(knitr)
library(kableExtra)
library(lubridate)
## call other scripts
source('mdhCovidWebScrape.R')
source('COVID.R')

## get data for the most recent date
dataWidePlain = dataWide %>% 
   filter(Date == last(Date))

dataLongAvgPlain = dataLongAvg %>% 
   filter(Date == last(Date), Variable == "PositivePercent")

dataLongAvgPeople = dataLongAvg %>% 
   filter(Date == last(Date), Variable == "PositivePercentPeoplePlot")

## zoom in range 
zoomRange = 60
dateBreak = "1 week"

```

## `r format(Sys.Date(), '%Y-%m-%d')`
* Testing
  + Total completed tests: **`r (dataWidePlain$Total.tested) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$Daily.tests) %>% formatC(format="d", big.mark=",")`)
  <!-- + Total people tested: **`r (dataWidePlain$Total.tested.people) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$Daily.tests.people) %>% formatC(format="d", big.mark=",")`) -->
  + Total positive cases: **`r (dataWidePlain$Total.cases) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$New.cases) %>% formatC(format="d", big.mark=",")`)
  + Daily/7-day positive percentage: **`r (round(dataLongAvgPlain$Value, 4)*100)`/`r (round(dataLongAvgPlain$movAvgValue, 4)*100)`**
  <!-- + Daily/7-day positive percentage (people): **`r (round(dataLongAvgPeople$Value, 4)*100)`/`r (round(dataLongAvgPeople$movAvgValue, 4)*100)`** -->
* Case info   
  + Patients who are currently sick: **`r (dataWidePlain$Currently.sick) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.sick <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.sick))) %>% formatC(format="d", big.mark=",")`)
  + Total deaths: **`r (dataWidePlain$Total.deaths) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.deaths <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.deaths)))`)
* Hospital admission/Vaccine  
  + Total accumulated hospitalized: **`r (dataWidePlain$Total.Hospital) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.hospitalized <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.hospitalized))) %>% formatC(format="d", big.mark=",")`)
    - Total accumulated ICU: **`r (dataWidePlain$Total.ICU) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.ICU <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.ICU)))`)
  + Total vaccine doses administered: **`r (dataWidePlain$Total.vaccine) %>% formatC(format="d", big.mark=",")`** (`r (ifelse(dataWidePlain$New.vaccine <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.vaccine))) %>% formatC(format="d", big.mark=",")`)
  + Total people with completed vaccination: **`r (dataWidePlain$Total.people.vaccine.completed) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$New.vaccine.people.completed) %>% formatC(format="d", big.mark=",")`)
  + Total people with one dose vaccination: **`r (dataWidePlain$Total.people.vaccine.onedose) %>% formatC(format="d", big.mark=",")`** (up `r (dataWidePlain$New.vaccine.people.onedose) %>% formatC(format="d", big.mark=",")`)

```{r plot1, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p1
p1+coord_cartesian(xlim = c(Sys.Date()-zoomRange, Sys.Date()), ylim=c(0, 9500))+
  scale_x_date(date_breaks = dateBreak, date_labels = "%b %d")+
  labs(subtitle = paste("Range:", zoomRange, "days"))
```

```{r plot2, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p2
p2+coord_cartesian(xlim = c(Sys.Date()-zoomRange, Sys.Date()))+
  scale_x_date(date_breaks = dateBreak, date_labels = "%b %d")+
  labs(subtitle = paste("Range:", zoomRange, "days"))
```
   
```{r plot3, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p3
p3+coord_cartesian(xlim = c(Sys.Date()-zoomRange, Sys.Date()))+
  scale_x_date(date_breaks = dateBreak, date_labels = "%b %d")+
  labs(subtitle = paste("Range:", zoomRange, "days"))
```

```{r plot5, echo=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p5
p5+coord_cartesian(xlim = c(Sys.Date()-zoomRange, Sys.Date()))+
  scale_x_date(date_breaks = dateBreak, date_labels = "%b %d")+
  labs(subtitle = paste("Range:", zoomRange, "days"))
```

```{r plot4, include=FALSE, warning = FALSE, message=FALSE}
## plots from COVID.R
p4
```

```{r plot6, echo=FALSE, message=FALSE, warning=FALSE}
## vaccination data
p6
```

```{r plot7, echo=FALSE, message=FALSE, warning=FALSE}
## vaccination data
p7
```


```{r table1, echo=FALSE, warning= FALSE, include = FALSE}
## table 1
 dataWide %>% 
   filter(Date %in% tail(Date, 5)) %>%
   mutate(Date = format(Date, format = "%b %d"))%>% 
   select(-contains("By"),-contains("Plot")) %>% 
   select(Date, starts_with("Total")) %>%
   rename_at(vars(starts_with("Total")), ~str_to_title(str_remove_all(.,"Total."))) %>%
   kable(digits = 3,booktabs = T, caption = "Cumulative numbers for last 5 days",align = "c") %>%
   kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 14) %>% 
   row_spec(5, color = "white", background = "#FF33CC") 
```


```{r table2, echo=FALSE, warning= FALSE}
## table 2 (added on 2021-10-14)
 breakThrough %>%
   kable(digits = 2, booktabs = T, caption = "COVID-19 Vaccine Breakthrough Weekly Update", align = "c",linesep = "") %>%
   kable_styling(latex_options = c("hold_position","scale_down"), font_size = 14) %>% 
   footnote(general = totalVacPeople$X2, general_title = paste0(totalVacPeople$X1 %>% str_replace("\\*",": ")),
                                                                 footnote_as_chunk = T) 
```


```{r table3, echo=FALSE, warning= FALSE}
## table 3
 dataWide %>%
   filter(Date %in% tail(Date, 7)) %>%
   mutate(Date = format(Date, format = "%b %d")) %>% 
   select(-starts_with("Total"), -ends_with("Percent"), Daily.tests, Daily.tests.people) %>% 
   rename(`Hospitalized` = Currently.hospitalized, `New case` = New.cases, `Tests` = Daily.tests, 
          `New people tested` = Daily.tests.people, 
          `New vaccince people completed` = New.vaccine.people.completed,
          `New vaccince people one dose` = New.vaccine.people.onedose) %>%
   select(Date, Hospitalized, ICU, `New case`, Tests, `New vaccince people completed`, `New vaccince people one dose`) %>% 
   mutate_at(vars(Hospitalized:`New vaccince people one dose`), list(~formatC(., format="d", big.mark=","))) %>%
   kable(digits = 2, booktabs = T, caption = "Current numbers for last 7 days", align = "c",linesep = "") %>%
   kable_styling(latex_options = c("hold_position","scale_down"), font_size = 14) %>%
   footnote(general = "https://github.com/coolbaby0208/MN-COVID19",general_title = "Source code: ",footnote_as_chunk = T) %>% 
   row_spec(7, color = "white", background = "#36688D")
```




